Covariates analysis of UFL-Mayo-ISB RNASeq data of cerebellum tissue (realigned from synapse BAM with Picard-STAR-HTSeq)

### 2016-11-10 code/Rmd/Mayo_CBE_RNASeq_Realigned_SynBAM_StarHTSeq.Rmd
Minor change

```{r dataExplore, fig.width = 6, fig.height = 15}
my.theme <- theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))

@@

### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=16, fig.width=16}
# Fit contrast
contrast = makeContrasts(contrasts=c("BrainRegion.DiagnosisCER_Control-BrainRegion.DiagnosisCER_AD",
                                     "BrainRegion.DiagnosisCER_Control-BrainRegion.DiagnosisCER_Pathologic_Aging",
                                     "BrainRegion.DiagnosisCER_Control-BrainRegion.DiagnosisCER_PSP",
                                     "BrainRegion.DiagnosisCER_Pathologic_Aging-BrainRegion.DiagnosisCER_AD",
                                     "BrainRegion.DiagnosisCER_PSP-BrainRegion.DiagnosisCER_AD",
                                     "BrainRegion.DiagnosisCER_PSP-BrainRegion.DiagnosisCER_Pathologic_Aging"),
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

>>>>

```{r dataExplore, fig.width = 10, fig.height = 6}
my.theme <- theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))

@@

### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=8, fig.width=20}
# Fit contrast
contrast = makeContrasts(contrasts=c("BrainRegion.DiagnosisCER_Control-BrainRegion.DiagnosisCER_AD",
                                     "BrainRegion.DiagnosisCER_Control-BrainRegion.DiagnosisCER_Pathologic_Aging",
                                     "BrainRegion.DiagnosisCER_Control-BrainRegion.DiagnosisCER_PSP",
                                     "BrainRegion.DiagnosisCER_Pathologic_Aging-BrainRegion.DiagnosisCER_AD",
                                     "BrainRegion.DiagnosisCER_PSP-BrainRegion.DiagnosisCER_AD",
                                     "BrainRegion.DiagnosisCER_PSP-BrainRegion.DiagnosisCER_Pathologic_Aging"),
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
